Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 algorithm_regret.tex
adding some comments

\dkedit{
For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
The remaining phases are the ones with
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.
Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
in expectation by Lemma~\ref{lem:phase-length},
and each step incurs regret at most \MAXR.
The total expected regret incurred in these phases is at most
$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3 \TieCutoff^3$.}

>>>>

\dkedit{
For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
The remaining phases are the ones with
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.}
\pfcomment{Is there a typo in the previous line?  Shouldn't it be 
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 / \TieCutoff^2$?
Or am I missing something?}
\dkedit{Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
in expectation by Lemma~\ref{lem:phase-length},
and each step incurs regret at most \MAXR.
The total expected regret incurred in these phases is at most
$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3 \TieCutoff^3$.}

### 2018-06-05 problem_setting.tex
adding some comments

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
Notice that based on Assumption~\ref{A1} below,
  \Best{\AgV} and \Second{\AgV} are unique with probability 1.
\pfcomment{Why is \Second{\AgV} unique with probability 1?  I don't think that is implied.  Can I remove that part of the statement?}
\dkcomment{It is unique with probablity 1 over the draw of agent types
  because for z=0, Assumption~\ref{A1} says that there is a measure 0
  set of agents whose difference between the best and second-best
  option is z=0. Or am I misunderstanding something?}

@@

\begin{assumption}[Not too many near-ties] \label{A1}
Near-ties have vanishing probability; 
that is, there exist constants \dkedit{$\TieCutoff > 0, \TieDensity$} such that 
$\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.
\end{assumption}

\dkdelete{
% The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
%is not restrictive.
%Because \TieDensity and \TieCutoff are both constants,
%we could simply increase \TieDensity.
%Perhaps even more simply, $\MinProb \leq 1/\ARMNUM$,
%while \TieCutoff is a constant,
%so an alternative is to decrease \MinProb by a suitable constant factor.
}

@@

\paragraph{Roles of parameters:}
Our problem setting is characterized by many parameters.
Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
the key parameters, \dkedit{and also give some prominence to
\TieDensity to illustrate an interesting phenomenon.}
On the other hand, we consider
$\sigma, \Diam, d$, and \TieCutoff to be constant.
We track all parameters through most of our proofs,
but report final results in terms of only the key parameters,
except where we illustrate a specific point.
In particular, we consider $d$ a constant, because users
typically evaluate products (or restaurants, etc.) by a small number of
relevant features.

>>>>

To support the formulation of our results and the analysis,
we define the following additional notation.
We let
$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
and
$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
denote the (indices of) the best and second-best arms for an agent
with attribute vector \AgV,
breaking ties arbitrarily (but consistently).
Notice that based on Assumption~\ref{A1} below,
  \Best{\AgV} and \Second{\AgV} are unique with probability 1.
\pfcomment{Why is \Second{\AgV} unique with probability 1?  I don't think that is implied.  Can I remove that part of the statement?}
\dkcomment{It is unique with probablity 1 over the draw of agent types
  because for z=0, Assumption~\ref{A1} says that there is a measure 0
  set of agents whose difference between the best and second-best
  option is z=0. Or am I misunderstanding something?}
  \pfcomment{That argument says that $\Best{\AgV}$ is unique.  But the second best, $\Second{\AgV}$, doesn't have to be.  The measure of the set of agents with 0 gap between the second- and third-best  options might not vanish.}

@@

\begin{assumption}[Not too many near-ties] \label{A1}
Near-ties have vanishing probability; 
that is, there exist constants $\TieCutoff > 0, \TieDensity$ such that 
$\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.
\end{assumption}

@@

\paragraph{Roles of parameters:}
Our problem setting is characterized by many parameters.
Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
the key parameters, and also give some prominence to
\TieDensity to illustrate an interesting phenomenon.
On the other hand, we consider
$\sigma, \Diam, d$, and \TieCutoff to be constant.
We track all parameters through most of our proofs,
but report final results in terms of only the key parameters,
except where we illustrate a specific point.
In particular, we consider $d$ a constant, because users
typically evaluate products (or restaurants, etc.) by a small number of
relevant features.
